Supplementary tables and figures for "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2022-06-18 src/docs_paper/tables-figures.Rmd
Doesn't need to be commented out anymore #128

<!-- \begin{figure}[h] -->
<!-- \centering -->
<!-- \makebox[\textwidth][c]{\includegraphics[page=13]{depends/temporal-interpolation-ribbon.pdf}} -->
<!-- \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Zimbabwe. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.} -->
<!-- \label{fig:temporal-interpolation-ribbon-13} -->
<!-- \end{figure} -->

>>>>

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=13]{depends/temporal-interpolation-ribbon.pdf}}
\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Zimbabwe. Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
\label{fig:temporal-interpolation-ribbon-13}
\end{figure}
